Synthesizing Symmetric Lenses

### 2018-07-06 papers/SymmetricLenses/main.tex
Comments on eval section

\subsection{Heuristic Usefulness}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMOpt{}: & \GreedySynth does not have any notion of cost, and searches for
              any lens that satisfies the specification. \\
\end{tabulary}

Figure~\ref{fig:heuristic} summarizes the result of this experiment.  We find
that \afm{TODO}.
% end evaluation

>>>>

\subsection{Heuristic Usefulness}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}

\begin{figure}
  \includegraphics{generated-graphs/metrics_importance}
  \caption{Number of benchmarks that synthesize the correct lens by a given
    algorithm. \NoTPOpt{} is the full symmetric synthesis algorithm, but
    termination parameters are ignored. \FCOpt{} provides a notion of cost to
    \GreedySynth, but once a satisfying lens is greedily found, that lens is
    returned. \NMCCOpt{} identifies the lens cluster in which the desired 
    lens lies.  \GreedySynth{} is then run on that cluster with no notion of
    cost. \NMOpt{} removes all notion of cost, and merely finds the first
    satisfying lens.\bcp{Am I reading this wrong, or does even the best
      algorithm fail to find the correct lens something like 20\% of the
      time?!?!?!}} 
  \label{fig:metric}
\end{figure}

Figure~\ref{fig:metric} summarizes the result of this experiment. We find that
our metrics are very important for finding the correct lens. Our
information-theoretic metric is critical for finding the correct lens. Indeed,
even when provided with the correct lens cluster, without a notion of cost, we
would need constrain our search space more with additional examples to find the
correct lens.

Our termination condition is also quite important. When running in \FCOpt{},
only 5 lenses are found. The first cluster in which a lens is found is rarely
the correct cluster. However, our termination condition is not perfect.
Sometimes users must tell the algorithm to ``keep going'' or ``stop early.''
Without termination parameters, our algorithm finds the correct lens for 36 of
our 45 benchmarks, 9 of them need help in the form of a termination parameter
for finding the correct lens.
% end evaluation
